\newcommand{\expheader}[5]{
  \large
  \begin{parcolumns}[colwidths={1=0.7\textwidth}]{2}
    \colchunk{\raggedright \textbf{#1} -- \textit{#2} -- #3}
    \colchunk{\raggedleft \textit{#4} -- \textit{#5}}
  \end{parcolumns}
  \normalsize
}

\cvsection{PROFESSIONAL EXPERIENCE}

\expheader{\href{https://capgemini.com/}{Capgemini}}
          {Senior Data Engineer}
          {Poland}
          {Aug 2023}
          {Present}

\textbf{FinTech Data Platform}
\cvexpspace
\begin{itemize}
  \cvitemsep
  \item Optimize data processing architecture using Databricks and Databricks Asset Bundles, improving efficiency.
  \item Architect Azure Pipelines for end-to-end data processing orchestration.
  \item Integrate Azure Data Factory pipelines, ensuring scalable and automated data workflows.
  \item Developed a robust testing framework, reducing release risks and enhancing deployment stability.
  \item Host Quarterly Planning and Retrospective sessions, enhancing team collaboration.
\end{itemize}

\smallskip

\textbf{Azure Upskilling Program --- Program Lead} \textit{(Mar 2025 -- Present)}
\cvexpspace
\begin{itemize}
  \cvitemsep
  \item Lead a Capgemini-wide Azure upskilling program for 1+ year, grown from Poland-only to international participation; onboarded 40+ specialists across intern, re-skilling, and cross-direction tracks on a rolling basis.
  \item Drove 80+ Microsoft certifications (AZ-900, DP-900) with a 100\% pass rate, backed by self-authored preparation guides.
  \item Re-designed 80\% of the curriculum into a hands-on-first format ($\sim$80\% of program time): 3--4 end-to-end assignments per participant covering Azure-native services, CI/CD, and Azure Databricks.
  \item Personally review every submission and host public demo sessions where participants present solutions to the active cohort.
  \item Enabled 20+ graduates to join Azure and Databricks projects, with interns regularly staffed before program completion.
\end{itemize}

\expheader{\href{https://nufa.ai/}{Mimesis Inc}}
          {Senior Data Engineer \& Co-Founder}
          {Armenia}
          {Jan 2021}
          {May 2023}

\smallskip

\textbf{AI-Driven Data Processing \& Infrastructure}
\cvexpspace
\begin{itemize}
  \cvitemsep
  \item Designed scalable data ingestion pipelines using AWS S3, AWS RDS, and Spark (PySpark).
  \item Led backend API development with Python and FastAPI, integrating data pipelines into the product architecture.
  \item Containerized ML and ETL workloads (Docker) and established Jenkins CI/CD, reducing operational overhead.
  \item Designed scalable cloud infrastructure for ML and data workflows, improving system resilience and flexibility.
\end{itemize}

\expheader{\href{https://www.epam.com/}{EPAM Systems}}
          {Data Engineer}
          {Belarus}
          {Jul 2019}
          {Sep 2021}

\smallskip

\textbf{ML-Driven eCommerce Optimization} \textit{(Sep 2020 -- Sep 2021)}
\cvexpspace
\begin{itemize}
  \cvitemsep
  \item Designed scalable Airflow-based data pipelines, ensuring efficient data flow and transformation.
  \item Optimized real-time data processing using Apache Spark and Kafka, reducing data latency and increasing performance.
\end{itemize}

\textbf{Enterprise BI \& Marketing Data Platforms} \textit{(Oct 2019 -- Jul 2020)}
\cvexpspace
\begin{itemize}
  \cvitemsep
  \item Developed ETL pipelines in Azure Data Factory and architected a star-schema warehouse model, optimizing Power BI analytics performance.
  \item Built a multi-zone Azure Blob Storage model with Azure Databricks pipelines and automated CI/CD (GitHub, Jenkins).
\end{itemize}
